School_drop_out

### 2021-02-02 School_drop_out.Rmd
Update the code for highschool drop-out.

wages <- as_tsibble(x = wages_hs2020,
                    key = id,
                    index = year,
                    regular = FALSE)

wages_do <- wages %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_1979 >= 19))
```

@@

```{r}
wages_hs_completed <- wages %>%
  filter(hgc == "12TH GRADE" &
           age_1979 < 19)
```

@@

wages_w <- as_tsibble(x = wages_hs2020_weighted,
                    key = id,
                    index = year,
                    regular = FALSE)

wages_do_w <- wages_w %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_1979 >= 19))
```

@@

```{r}
wages_hs_completed_w <- wages_w %>%
  filter(hgc == "12TH GRADE" &
           age_1979 < 19)
```

>>>>

wages <- as_tsibble(x = wages_hs2020,
                    key = id,
                    index = year,
                    regular = FALSE) %>%
  mutate(dob = 1979 - age_1979, 
         age_hgc = yr_hgc - dob)

wages_do <- wages %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))
```

@@

```{r}
wages_hs_completed <- wages %>%
  filter(hgc == "12TH GRADE" &
           age_hgc < 19)
```

@@

wages_w <- as_tsibble(x = wages_hs2020_weighted,
                    key = id,
                    index = year,
                    regular = FALSE) %>%
  mutate(dob = 1979 - age_1979, 
         age_hgc = yr_hgc - dob)

wages_do_w <- wages_w %>%
  filter((hgc %in% c("9TH GRADE", 
                    "10TH GRADE",
                    "11TH GRADE")) |
        (hgc == "12TH GRADE" & 
        age_hgc >= 19))
```

@@

```{r}
wages_hs_completed_w <- wages_w %>%
  filter(hgc == "12TH GRADE" &
           age_hgc < 19)
```
